Data analysis to support temporary cycleways

### 2020-05-04 README.Rmd
Add readme files

---
title: Data analysis to support temporary cycleways
output:
  github_document:
    toc: true
    toc_depth: 2
# uncomment the next line if no phantomjs
# always_allow_html: no
---

@@

>>>>

---
title: Data analysis to support temporary cycleways
output:
  html_document:
  # github_document:
    toc: true
    toc_depth: 2
# uncomment the next line if no phantomjs
# always_allow_html: no
---

@@

```{r, engine='zsh', eval=FALSE}
# deploy

```
